A word-sense representation for documents based on information value and word sense disambiguation

### 2014-04-04 paper/refactor.tex
fix typo

\begin{article}
\begin{abstract}
In this project we analyzed some Lenin works in order to identify the presence of some topics of his biography. To achieve this, we defined and implemented a simple metric distance between a word-sense and a document and confronted this metric using a evaluation set of word-senses against a reduced set of  documents with well known topics. During this work, we generated an indexed database of Lenin's complete works from a web site\cite{LENIN} and we applied a series of syntactic, semantic and lexicographic tools in order to model the similarity between a document and a word-sense. We applied information value\cite{DARWIN} and a simple algorithm of word sense disambiguation\cite{LESK} based on Wordnet\cite{WORDNET} in order to generate the \emph{top senses} (or principal senses) of a document. Finally, we compare them against some semantic senses of interest (for example: revolution, war, philosophy, etc). 
\end{abstract}

>>>>

\begin{article}
\begin{abstract}
In this project we analyzed some Lenin works in order to identify the presence of some topics of his biography. To achieve this, we defined and implemented a simple metric distance between a word-sense and a document and confronted this metric using a evaluation set of word-senses against a reduced set of  documents with well known topics. During this work, we generated an indexed database of Lenin's complete works from a web site\cite{LENIN} and we applied a serie of syntactic, semantic and lexicographic tools in order to model the similarity between a document and a word-sense. We applied information value\cite{DARWIN} and a simple algorithm of word sense disambiguation\cite{LESK} based on Wordnet\cite{WORDNET} in order to generate the \emph{top senses} (or principal senses) of a document. Finally, we compare them against some semantic senses of interest (for example: revolution, war, philosophy, etc). 
\end{abstract}
